\paragraph{}
Relations refers to existing Ocarina~\cite{HZP07} functions.\\
Note that each reference to \textit{an element} can be 
replaced by {a set}, since the function will really be 
applied to each elements of the parameter-passed sets. 
While all elements are in fact variables (in the meaning 
of a designator with fluctuating value), they are synonymous 
to their related set.\\
The range variable (ie. the element defined just after the 
\textbf{foreach} keyword) is an exception to this rule, and 
should always be refered as an element of the range set.\\
Of course, anonymous sets cannot be refered with their name 
either...

\subsubsection {Is\_Subcomponent\_Of}

\textit{Is\_Subcomponent\_Of} takes as parameters two elements,
and return true if the first element is an AADL instance which 
is a subcomponent of the second element.

\subsubsection {Is\_Bound\_To}

\textit{Is\_Bound\_To} takes as parameters two elements,
and return true if the first element is an AADL instance which 
is bound to the second element via the actual\_$*$\_binding 
property class, where $*$ can be either \textit{processor},
\textit{memory} or \textit{connection}.

\subsubsection {Is\_Connected\_To}

\textit{Is\_Connected\_To} takes as parameters two elements,
and return true if the first element is an AADL instance which 
is connected to the second element.

\subsubsection {Is\_Called\_By}

\textit{Is\_Called\_To} takes as parameters two elements,
and return true if the second element has a call sequence
with a subprogram call on the first element (which must be
a subprogram).

\subsubsection {Is\_Calling}

\textit{Is\_Calling} takes as parameters two elements,
and return true if the first element has a call sequence
with a subprogram call on the second element (which must 
be a subprogram).

\subsubsection {Is\_Accessed\_By}

\textit{Is\_Accessed\_By} takes as parameters two elements,
and return true if the first element is an AADL instance which 
is accessed by the second element, either directly or not.

Note that \textit{Is\_Accessed\_By} can be used with a 
connection instance and a data instance, returning true if the
connection's destination is actually the provided data, and false 
elsewhere.

\subsubsection {Is\_Accessing\_To}

\textit{Is\_Accessing\_To} is the same as \textit{Is\_Accessed\_By}, 
but returns the instances which are accessing (ie. elements of
the second parameter) instead of the instances which are accessed.

\subsubsection {Is\_Passing\_Through}

\textit {Is\_Passing\_Through} returns the end to end flows which are passing
through the provided component instance.
